The Castro AMR Simulation Code: Current and Future Developments

### 2019-10-10 astronum_2019_Castro/astronum-castro-2019.tex
revise awkward train of and :-)

Altogether, these developments will allow us to begin our first
three-dimensional realistic XRB calculations by the end of the year,
with parameter studies to follow.  These calculations will help us
understand the nucleosynthesis during XRBs and its impact on
observables and the interpretation of lightcurves and neutron star
structure.

>>>>

Altogether, these developments will allow us to begin our first
three-dimensional realistic XRB calculations by the end of the year,
with parameter studies to follow.  These calculations will help us
understand the nucleosynthesis during XRBs and its impact on
observables along with the interpretation of lightcurves and neutron star
structure.
